\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{enumitem}

\begin{document}

\title{Resume}
\author{Your Name}
\date{\today}
\maketitle

\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Web Development Intern}
    \begin{itemize}
        \item Completed a remote internship where I developed websites using HTML, CSS, and JavaScript, gaining practical experience in front-end development.
    \end{itemize}
    
    \item \textbf{Hackathon Winner}
    \begin{itemize}
        \item Led a team to victory in a regional hackathon by developing a web application using PHP and React, showcasing problem-solving and teamwork skills.
    \end{itemize}
    
    \item \textbf{Community Service Volunteer}
    \begin{itemize}
        \item Collaborated with a local non-profit organization to build a website, demonstrating a commitment to giving back to the community.
    \end{itemize}
\end{itemize}

\section*{Work Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Data Engineer}
    \begin{itemize}
        \item Taiyo.ai, San Francisco, California, USA (06/2022 - 09/2022)
        \item Conducted web scraping to extract data from both the World Bank and IADB websites.
        \item Python scripting in OOP and establishment of a robust data pipeline for integration with Google Cloud.
        \item Data preprocessing, data analysis using Pandas, NumPy, Matplotlib, and Seaborn.
    \end{itemize}
    
    \item \textbf{Prompt Engineer}
    \begin{itemize}
        \item Scale AI, Remote (09/2023 - 02/2024)
        \item Reviewed LLM model code generation. Data science and ML training expert improved prompt generative AI model for better performance.
    \end{itemize}
\end{itemize}

\end{document}