\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

\definecolor{myblue}{RGB}{0, 89, 163}
\definecolor{mygray}{RGB}{128, 128, 128}

\begin{document}

\begin{center}
    \textbf{\LARGE Rohit Kumar}
    
    \textit{B.Tech in Artificial Intelligence}
    
    Sarala Birla University, Ranchi, Jharkhand
\end{center}

\section*{Education}
\textbf{B.Tech in AI (Artificial Intelligence)} from Sarala Birla University \\
\textbf{Expected Graduation:} April 2025

\section*{Programming Languages}
\textcolor{myblue}{\textbf{Python}}, \textcolor{myblue}{\textbf{C++}}, \textcolor{myblue}{\textbf{C}}, \textcolor{myblue}{\textbf{Java}}, \textcolor{myblue}{\textbf{JavaScript}}, \textcolor{myblue}{\textbf{C sharp}}

\section*{Libraries and Tools}
\textcolor{myblue}{\textbf{Tensorflow}}, \textcolor{myblue}{\textbf{HuggingFace}}, \textcolor{myblue}{\textbf{Langchain}}, \textcolor{myblue}{\textbf{PyTorch}}, \textcolor{myblue}{\textbf{Sklearn}}, \textcolor{myblue}{\textbf{Pandas}}, \textcolor{myblue}{\textbf{Numpy}}, \textcolor{myblue}{\textbf{OpenCV}}, \textcolor{myblue}{\textbf{LLM}}, \textcolor{myblue}{\textbf{Flask}}, \textcolor{myblue}{\textbf{React}}, \textcolor{myblue}{\textbf{NLP}}, \textcolor{myblue}{\textbf{Node.js}}, \textcolor{myblue}{\textbf{Android App Development}}, \textcolor{myblue}{\textbf{SQL}}, \textcolor{myblue}{\textbf{ETL}}, \textcolor{myblue}{\textbf{IoT}}, \textcolor{myblue}{\textbf{ESP32}}, \textcolor{myblue}{\textbf{Arduino}}, \textcolor{myblue}{\textbf{Git}}, \textcolor{myblue}{\textbf{Firebase}}, \textcolor{myblue}{\textbf{MongoDB}}, \textcolor{myblue}{\textbf{Linux}}, \textcolor{myblue}{\textbf{Neural Network}}, \textcolor{myblue}{\textbf{CUDA}}, \textcolor{myblue}{\textbf{NoSQL}}, \textcolor{myblue}{\textbf{Docker}}

\section*{ML Architectures}
\textcolor{myblue}{\textbf{CNN}}, \textcolor{myblue}{\textbf{YOLO}}, \textcolor{myblue}{\textbf{Transformers (BERT, LSTM)}}

\section*{Additional Information}
\textbf{Passionate Machine Learning and Android App Developer from India} \\
\textbf{Actively seeking opportunities in ML/AI and Data Science} \\
\textbf{Contact Email:} rohitcode005@gmail.com \\
\textbf{GitHub:} \textcolor{myblue}{\underline{\href{https://github.com/Rohitw3code}{Rohitw3code}}} \\
\textbf{LinkedIn:} \textcolor{myblue}{\underline{\href{https://www.linkedin.com/in/rohit-kumar-66522518a/}{Rohit Kumar on LinkedIn}}}

\section*{Relevant Projects}
\textbf{AI ResumeRover (LLM langchain) (09/2023)}
\begin{itemize}
    \item Developed a platform for HR to upload and manage resumes efficiently. Utilized Langchain, OpenAI, FAISS, Python, and Streamlit.
    \item Enhanced skills in data management, AI integration, and HR processes.
\end{itemize}

\textbf{MedDiag: AI-Powered Disease Diagnosis and Doctor Report Summary (02/2024)}
\begin{itemize}
    \item Created a web app for disease prediction using deep learning with CNN. Supported image classification and doctor report summarization.
    \item Advanced knowledge in healthcare technology and AI application in medical diagnosis.
\end{itemize}

\textbf{(Reinforcement Learning) AI Maze Solver: Q-Learning Project (03/2024)}
\begin{itemize}
    \item Developed a maze game using the Q-Learning Algorithm in Python pygame.
    \item Improved skills in reinforcement learning algorithms and game development.
\end{itemize}

\textbf{Object Detection from Scratch YOLO (01/2024)}
\begin{itemize}
    \item Built an end-to-end pipeline for real-time object detection using Tensorflow, numpy, matplotlib, and opencv.
    \item Expanded expertise in computer vision and deep learning applications.
\end{itemize}

\textbf{Speech Emotion Detection (08/2023)}
\begin{itemize}
    \item Created a website for emotional state prediction from user speech.
    \item Gained experience in speech analysis and emotion classification.
\end{itemize}

\section*{Extracurricular Activities}
\textbf{Machine Learning Club President}
\begin{itemize}
    \item Organized weekly meetings to discuss the latest trends in machine learning and AI.
    \item Led a team to develop a machine learning project that achieved top 3 in a regional competition.
    \item Dates: September 2021 - May 2022
\end{itemize}

\textbf{Hackathon Participant}
\begin{itemize}
    \item Participated in a 24-hour hackathon focused on developing innovative solutions for sustainability.
    \item Collaborated with a diverse team to create a mobile app prototype for tracking carbon footprint.
    \item Dates: November 2021
\end{itemize}

\textbf{Volunteer at Local Coding Bootcamp}
\begin{itemize}
    \item Assisted instructors in teaching coding basics to underprivileged youth in the community.
    \item Provided mentorship and guidance to students during coding projects.
    \item Dates: January 2022 - Present
\end{itemize}

\textbf{STEM Outreach Program Volunteer}
\begin{itemize}
    \item Presented STEM concepts to elementary school students through interactive workshops.
    \item Facilitated hands-on experiments to spark interest in science and technology.
    \item Dates: October 2021 - December 2021
\end{itemize}

\textbf{Data Science Intern at XYZ Tech}
\begin{itemize}
    \item Implemented data extraction techniques to gather insights from large datasets.
    \item Collaborated with the research team to analyze and interpret research findings.
    \item Dates: June 2021 - August 2021
\end{itemize}

\end{document}